Formal Modelling of Predator Preferences using Molecular Gut-Content Analysis

### 2016-03-01 paper/main.tex
attempted to unify syntax; added citation to vignette; removed some useless parameters; changed my email address

\documentclass[smallextended]{svjour3}
\input{TexOpts.tex}
\begin{document}
\title{Formal Modelling of Predator Preferences using Molecular Gut-Content Analysis}
\author{Edward A. Roualdes \and Simon J. Bonner \and Thomas D. Whitney \and James D. Harwood}
\institute{E. A. Roualdes 
        \at Department of Mathematics and Statistics, California State University, Chico, Chico, CA 95929, USA \\ \email{eroualdes@csuchico.edu}
        \and S. J. Bonner
        \at Department of Statistical and Actuarial Sciences, University of Western Ontario, 1151 Richmond Street, London, Ontario, N6A 5B7, Canada
        \and T.D. Whitney 
        \at Department of Entomology, University of Kentucky, Lexington, KY 40546, USA \emph{Present address: Warnell School of Forestry and Natural Resources, University of Georgia, Athens, GA 30602, USA}
        \and
        J.D. Harwood
        \at Department of Entomology, University of Kentucky, Lexington, KY 40546, USA
}

>>>>

\documentclass[smallextended]{svjour3}
\input{TexOpts.tex}
\begin{document}
\title{Formal Modelling of Predator Preferences using Molecular Gut-Content Analysis}
\author{Edward A. Roualdes \and Simon J. Bonner \and Thomas D. Whitney \and James D. Harwood}
\institute{E. A. Roualdes 
        \at Department of Statistics, University of Kentucky, Lexington, KY 40506, USA \emph{Present address: Department of Mathematics and Statistics, California State University, Chico, Chico, CA 95929, USA} \\ \email{eroualdes@csuchico.edu}
        \and S. J. Bonner
        \at Department of Statistics, University of Kentucky, Lexington, KY 40506, USA \emph{Present address: Department of Statistical and Actuarial Sciences and Department of Biology, University of Western Ontario, 1151 Richmond Street, London, Ontario, N6A 5B7, Canada}
        \and T.D. Whitney 
        \at Department of Entomology, University of Kentucky, Lexington, KY 40546, USA \emph{Present address: Warnell School of Forestry and Natural Resources, University of Georgia, Athens, GA 30602, USA}
        \and
        J.D. Harwood
        \at Department of Entomology, University of Kentucky, Lexington, KY 40546, USA
}
